---
author: "José R. Ferrer Paris"
title: "This is how we built this!"
editor_options: 
  chunk_output_type: console
---

## No place like home

This is a test of a personal website for [jrfep](https://jrfep.github.io/).

These instructions are in English, but this site has content in multiple languages... I know it is confusing, but this is how I work. If you require clarifications please open an issue or send me a message. 

All files are available in a [GitHub repository](https://github.com/jrfep/jrfep.github.io).  The `mostly-harmless` branch uses [Quarto](https://quarto.org/docs/websites/) to build the site.




## Render site


With quarto and RStudio we can open the Build tab and select Build Website...

Or we can go to the command line and render the site: 

```{sh}
#| eval: false
quarto render 
```

Sing [All the rowboats](https://youtu.be/2CZ8ossU4pc) in the meantime (optional).

And then launch a preview:

```{sh}
#| eval: false
quarto preview
```

If this work, we can just `git add`, `git commit` and `git push` it to the repo and see the changes!



## Just in case

![ [Stand back, I know regular expressions.](https://xkcd.com/208/)](https://imgs.xkcd.com/comics/regular_expressions.png)


[^1]: Yes, I use this [weird spelling...](https://english.stackexchange.com/questions/230494/should-i-always-use-the-ised-ending-for-uk-english-and-the-ized-for-us)

## Prepare data for some pages

### Flexdashboard and iNaturalist

To get the data I first install the `rinat` package:

```{r}
#| eval: false
here::i_am("how2/how-to-site.qmd")
if (!require(rinat)) {
  install.packages("rinat")
  library(rinat)
}
```

Then I can download the observations from iNaturalist and save them in a data folder:

```{r}
#| eval: false
# Download observations and save to RDS file
user_obs <- get_inat_obs_user("NeoMapas",maxresults = 5000)
if (!dir.exists(here::here("data")))
    dir.create(here::here("data"))
file_name <- here::here("data","iNaturalist-obs-NeoMapas.rds")
saveRDS(file=file_name, user_obs)

```


### Photos from Flickr

So, I think I need some photos in my website, and I have a Flickr account, and I use R, there should be a library that...

Oh yes! found it!

<https://koki25ando.github.io/FlickrAPI/>

```{r}
#| eval: false
install.packages("FlickrAPI")
```

Now I need a [Flickr API key](https://www.flickr.com/services/developer/) 

```{r}
#| eval: false
library(FlickrAPI)
setFlickrAPIKey(api_key = "YOUR_API_KEY_HERE", install = TRUE)
```

And finally, it works!

Let's now query our photos (up to 1000) and save the information in a RDS file:

```{r}
#| eval: false
here::i_am("how2/how-to-site.qmd")
library(FlickrAPI)
library(foreach)
library(dplyr)
readRenviron("~/.Renviron") # read the API key
here::i_am("how2/how-to-site.qmd")
photos <- foreach(u=c("jferrer","jferrer","199798864@N08"), i=c(1,2,1),.combine = "bind_rows") %do% {
  getPhotos(user_id = u, img_size="m", extras = c("description","owner_name",
  "url_m"), per_page=1000, page=i)
}

dim(photos)

file_name <- here::here("data","flickr-photos.rds")
saveRDS(file=file_name, photos)
```

### Photos from google 

### Galleries with `pixture`

I am experimenting with the [pixture package](https://www.royfrancis.com/pixture/index.html) to create image galleries.

```{r}
#| eval: false
install.packages(c("htmlwidgets","shiny","remotes"))
remotes::install_github('royfrancis/pixture')
```

### Bibliography

Download one `csl` as a base style

```{.bash}
cd bibteX
wget 'https://www.zotero.org/styles/journal-and-proceedings-of-the-royal-society-of-new-south-wales?source=1' --output-document=my.csl
```

Modify sort order of the bibliography (not the citation...):

```{.xml}
<bibliography hanging-indent="true" entry-spacing="0">
    <sort>
      <key variable="issued" sort="descending"/>
      <key macro="author"/>
    </sort>
  ...
```

