---
title: Ecological Society of Australia 2023
date: July 2023
categories:
  - Australia
  - Congreso
  - Nacional
  - Ponente
  - Ecología del fuego
  - Rpubs
  - OSF
---

# ESA 2023

Conference of the Ecological Society of Australia. 3–7 Julio 2023, [Darwin](/lgrs/Darwin.qmd), Northern Territory

```{r}
library(pixture)
library(dplyr)
here::i_am("lgrs/Caracas.qmd")
source(here::here("inc", "functions.R"))
```


```{r}
#| output: asis
slc <- c("David @ ESA2023 in Darwin")
photos <- filter_flickr_photo(seleccion = slc) |>
    pull_flickr_paths_captions(howmany = 1, preview = TRUE)

cat(sprintf("<center>\n%s\n<br/>\n%s<br/></center>", 
         photos$paths, photos$captions))
```


## Logo

<img src="events/logos/ESA2023-logo.svg" style="background-color: #13032333;" width=303/>

## Enlaces

- [Página web](https://esa2023.org.au)
- [Programa de la conferencia](https://esa2023.org.au/conference-program/)

## Presentación y productos relacionados

- **Fire ecology traits of Australian plants: Creating a database to summarise scientific knowledge about plant response to fire events**. Por: Dr José Rafael Ferrer-Paris, University of New South Wales. [Presentación en `RPubs`](https://rpubs.com/jrfep/firevegdb-ESA2023)

Relacionado con el proyecto de la base de datos de respuestas de la vegetación al fuego:

> Ferrer-Paris, J. R. and Keith, D. A. (2022) Fire Ecology Traits for Plants: A database for fire research and management. Version 1.00. Centre for Ecosystem Science, University of New South Wales, Sydney, Australia. Retrieved from osf.io/hu96w